Icicle: a single-pass query language

### 2015-11-24 2016icicle/Main.tex
related work: lustre

\authorinfo{
  Amos Robinson$^\dagger$$^\ddagger$
  \and Huw Campbell$^\ddagger$
  \and Mark Hibberd$^\ddagger$
  \and Tran Ma$^\ddagger$
  \and Jacob Stanley$^\ddagger$
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{amosr@cse.unsw.edu.au}
  }
  \shortstack{
    $^\ddagger$Ambiata      \\
    Big data and shit       \\[2pt]
    \textsf{\{first.last\}@ambiata.com}
  }
}

@@

\section*{Acknowledgements}
I would like to thank all of Ambiata for allowing me to work on such an interesting and useful problem, and on top of that being the most sensible group of people I have ever had the pleasure of working with.

>>>>

\authorinfo{
  Amos Robinson$^\dagger$$^\ddagger$
  \and Ben Lippmeier$^\dagger$
  \and Tran Ma$^\ddagger$
  \and Jacob Stanley$^\ddagger$
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{amosr,benl@cse.unsw.edu.au}
  }
  \shortstack{
    $^\ddagger$Ambiata      \\
    Big data and shit       \\[2pt]
    \textsf{\{first.last\}@ambiata.com}
  }
}

@@

\input{section/XX-Related-DataFlow.tex}

\section*{Acknowledgements}
I would like to thank all of Ambiata, particularly Huw Campbell and Mark Hibberd.
